Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils

### 2016-03-31 manuscript/cpcrw_manuscript.Rmd
Fixed outlier reporting

```{r compute_excludes, echo=FALSE}
# Compute outlier and exclusion numbers
# TODO: this isn't good--fragile if files move or change names
# Want everything in-memory (or something)
rn <- readLines("../outputs/3-remove/removed_data.csv") %>% length
sdn <- readLines("../outputs/summarydata.csv") %>% length
fluxn <- nrow(fluxdata)
en <- sum(fluxdata$outlier)
```

Anomalous data were excluded based on their being more than `r CO2_EXCLUDE_DEVS` (for CO~2~) or `r CH4_EXCLUDE_DEVS` (for CH~4~) mean absolute deviations {Davies, 1993 #3138} from the treatment mean within a 10-day period, treatment, and temperature. We excluded `r en` of `r fluxn` (`r round(en/fluxn*100)`%) of the gas flux measurements for this reason. Other data (`r round(rn/sdn*100)`%) were removed because of known instrument problems, e.g. the analyzer was left running after leaving a chamber. The final number of valid flux samples from the 100-day incubation was `r sum(!fluxdata$outlier)`.

>>>>

```{r compute_excludes, echo=FALSE}
# Compute outlier and exclusion numbers
# TODO: this isn't good--fragile if files move or change names
# Want everything in-memory (or something)
rn <- readLines("../outputs/3-remove/removed_data.csv") %>% length
sdn <- readLines("../outputs/summarydata.csv") %>% length
fluxn <- nrow(fluxdata)
```

Anomalous data were excluded based on their gas fluxes being more than `r CO2_EXCLUDE_DEVS` (for CO~2~) or `r CH4_EXCLUDE_DEVS` (for CH~4~) mean absolute deviations {Davies, 1993 #3138} from the treatment mean within a 10-day period, for a given treatment and temperature. We excluded `r outlier_count` of `r fluxn` (`r pn(outlier_count/fluxn*100, 1)`%) measurements for this reason. Other data (`r pn(rn/sdn*100, 1)`%) were removed because of known instrument problems, e.g. the analyzer was left running after leaving a chamber. The final number of valid flux samples from the 100-day incubation was `r sum(!fluxdata$outlier)`.
